Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-07-10 main.tex
Minor fixes in Diego study

@@

@@

Overall, Vincent provided 154 demonstrations to the robot, and he remained
actively engaged over the four weeks. The story was well accepted by Vincent and
he seriously engaged into the game. After the first week, he showed good
confidence to play with the robot and he built affective bonds with the robot
over the course of the study, as evidenced by some cries on the last session,
and several letters sent by him to the robot \emph{after} the end of the study
(one of them 4 months later) to get news. This represents a promising initial
result: we can effectively keep a child engaged with the robot for a relatively
long period of time (about 5 hours).

No conclusion can be drawn in terms of actual handwriting remediation: we did
not design this study to formally assess possible improvements.

However, as pictured on Figure~\ref{fig:stimuli}, Vincent was able to
significantly improve the robot's skill, and he acknowledged that he had been
able to help the robot: in that regard, Vincent convinced himself that he was
``good enough'' at writing to help someone else, and this is likely to have
positively impacted his self-esteem.

>>>>

\paragraph{Context, Study Design}

@@

\paragraph{Results}

@@

Overall, Vincent provided 154 demonstrations to the robot, and he remained
actively engaged over the four weeks. The story was well accepted by Vincent and
he seriously engaged into the game. After the first week, he showed good
confidence to play with the robot and he built affective bonds with the robot
over the course of the study, as evidenced by some cries on the last session,
and a letter sent by him to the robot 4 months \emph{after} the end of the study
to get news. This represents a promising initial result: we can effectively keep
a child engaged with the robot for a relatively long period of time (about 5
hours).

No conclusion can be drawn in terms of actual handwriting remediation: we did
not design this study to formally assess possible improvements.  However, as
pictured on Figure~\ref{fig:stimuli}, Vincent was able to significantly improve
the robot's skill, and he acknowledged that he had been able to help the robot:
in that regard, Vincent convinced himself that he was ``good enough'' at writing
to help someone else, and this is likely to have positively impacted his
self-esteem.
